---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(summary.welch)
y <- rnorm(20)
x1 <- rbinom(20, 1, .7)
x2 <- rbinom(20, 1, .7)
z <- rnorm(20)
```

# summary.welch
When using summary.welch, for every predictor, you must specify all binary predictors that it interacts with in your model. 

For example, if this is your model:

```{r}
f <- y~x1*z + x2*z
f
```

x1 interacts with z (not binary, so you aren't required to specify it), z interacts with x1 and x2 (both are binary, so both must be specified), and x2 interacts with z (not binary, so you aren't required to specify it).

Specify interacting partners like this:

```{r}
preds_interacting <- list(x1="z", 
     z=c("x1","x2"),
     x2="z")
preds_interacting
```

If you do not specify the names of the predictors in your list, summary.welch will assume you are going by model.frame's order
```{r}
mod <- lm(f)
colnames(model.frame(f))[-1]
```
